Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Removed redundant loaded packages

```{r}
#' load packages
library('tidyverse')
# library('xlsx')
library('scales')
library('stringr')
library('conflicted')
library('Hmisc')
library('kableExtra')

#resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```

>>>>

```{r}
#' load packages
library("tidyverse")
library("scales")
library("conflicted")
library("knitr")

# Resolve package function conflicts
conflict_prefer('filter', 'dplyr')
conflict_prefer('select', 'dplyr')
conflict_prefer('kable', 'knitr')
```
